\Large{Adversarial Training against Systematic Uncertainty}

### 2016-09-11 tex/paper.tex
save
related work

\documentclass[twocolumn,preprintnumbers,superscriptaddress,nofootinbib,aps,floatfix,letterpaper]{revtex4-1}

@@

\glnote{Distinction between statistical and systematic uncertainty.}
\glnote{Define nuisance parameters.}
\glnote{We want to build an accurate classifier whose output remains invariant with
respect to systematic uncertainties.}
% https://www.slac.stanford.edu/econf/C030908/papers/TUAT004.pdf
\glnote{Motivate the criterion (which may not be obvious for the ML crowd). See pivotal quantity motivation.}

@@

@@

\glnote{Define the architecture of $r$ when $Z$ is categorical ($r$ is a
standard classifier) or continuous ($r$ is e.g a 2-output NN such that the
distribution of $Z|f(X)$ is modeled by a truncated gaussian of known support).}

@@

\glnote{Alternative to learning a parameterized classifier for LLR.}
\glnote{Similar to domain adaptation, but with infinitely many domains,
as parameterized by $Z$, also related to transfer learning.}
\glnote{Other applications: removing implicit bias in data (e.g. gender bias).}

@@

\begin{acknowledgments}
The authors would like to thank...
\end{acknowledgments}

>>>>

\documentclass[twocolumn,superscriptaddress,aps]{revtex4-1}

@@

\glnote{Distinction between statistical and systematic uncertainty.}
\glnote{Outline taxonomy of uncertainties.}
\glnote{Define nuisance parameters. See refs in Noel's papers.}
\glnote{We want to build an accurate classifier whose output remains invariant with
respect to systematic uncertainties.}
% https://www.slac.stanford.edu/econf/C030908/papers/TUAT004.pdf
\glnote{Motivate the criterion (which may not be obvious for the ML crowd). See pivotal quantity motivation.}
\glnote{Discuss what kind of uncertainties the proposed approach is good for.}

@@

\glnote{Add summary figure.}

@@

\subsection{Toy example}

\glnote{Define the architecture of $r$ when $Z$ is categorical ($r$ is a
standard classifier) or continuous ($r$ is e.g a 2-output NN such that the
distribution of $Z|f(X)$ is modeled by a truncated gaussian of known support). Cite Nix.}

\subsection{Physics example}

@@

To account for systematic uncertainties, experimentalists in high energy physics
typically take as fixed a classifier $f$ built from training data for a nominal
value $z_0$ of the nuisance parameter, and then propagate uncertainty
\glnote{add ref} by estimating $p(f(x)|z)$ with a parameterized calibration
procedure. Clearly, this classifier is however not optimal for $z \neq z_0$. In
this setting, parameterized
classifiers~\citep{cranmer2015approximating,Baldi:2016fzo} directly take
(nuisance) parameters as additional input variables, hence ultimately providing
the most statistically powerful approach for incorporating the effect of
systematics on the underlying classification task.  As argued in
\citep{Neal:2007zz}, such classifiers can however not be used on real data since
the correct value $z$ of the nuisance often remains unknown. This is typically
not an issue in the context of parameter
inference~\citep{cranmer2015approximating}, where nuisance parameters are
marginalized out, but otherwise often limits the range of their applications. In
practice, parameterized classifiers  are also often computationally expensive to
build and evaluate. In particular, calibrating their decision fucntion, i.e.
approximating $p(f(x,z)|z)$ as a continuous function of $z$, remains an open
challenge. By contrast, constraining $f$ to be pivotal yields a classifier which
may not be optimal, as discussed in Section~\ref{sec:theory}, but that can be
used in a wider range of applications, since knowing the correct value $z$ of
the nuisance is not necessary, and for which calibration needs to be carried out
only once, since  the dependence on the nuisance is now built in the classifier.
\glnote{Shall we also discuss the relation with \citep{Neal:2007zz} where point
estimates of the nuisance are used as inputs to $f4$?}

In machine learning, the proposed method can be related to the problem of domain
adaptation
\citep{blitzer2006domain,pan2011domain,gopalan2011domain,gong2013connecting,baktashmotlagh2013unsupervised,ganin2014unsupervised},
where the goal is often stated as trying to learn a domain-invariant
representation of the data. Similarly, our method also relates to the problem of
enforcing fairness in classification \citep{zemel2013learning,EdwardsS15}. For
both families of methods, the problem can equivalently be stated as learning a
classifier which is a pivotal quantity with respect to either the domain or some
chosen attribute of the data, such as gender, color or age. In this context,
\citep{EdwardsS15} is certainly among the closest to our work, in which fairness
is enforced through an adversarial minimax setup composed of a classifier and an
adversary discriminator. In particular, our work can be regarded as a
generalization that also supports the continuous case, which can be viewed as
handling infinitely many domains, provided they can be continuously
parameterized, or as enforcing fairness over continuous attributes.

@@

\begin{acknowledgments}
\end{acknowledgments}
